Generative adversarial neural networks model of photonic crystal fiber based Surface Plasmon Resonance Sensor

### 2020-10-03 docs/paper/paper.tex
update: loss_curve::Bar-chart

\begin{figure}
	\begin{subfigure}{.48\textwidth}
		\centering
		\begin{tikzpicture}
		\begin{axis}[
		xlabel=Epochs, 
		ylabel=Training \space MSE,
		width=\textwidth,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		ymax=3,
		height=6cm,
		no marks
		]
		\addplot[line width=1pt,solid,color=blue] %
		table{data/ann_tr_loss_3k_their_data_without.txt};
		\addlegendentry{Without GAN}

		\addplot[line width=1pt,solid,color=red] %
		table{data/ann_tr_loss_3k_their_data_with.txt};
		\addlegendentry{With GAN}
		\end{axis}
		\end{tikzpicture}
	\end{subfigure}

@@

\begin{figure}
	\centering
	\begin{tikzpicture}[]
	\begin{axis}[
	ybar, axis x line=bottom, xlabel=Augmented samples, 
	xmin=-100,xmax=2100,
	ymin=0,ymax=1,
	width=0.48\textwidth, height=5cm,
	axis y line=left, ylabel=MSE, 
	legend cell align=left,
	legend style={draw=none, at={(0.5,-0.25)},anchor=north,/tikz/every even column/.append style={column sep=1.0cm}}, 
	ylabel near ticks, ylabel shift={-5pt},
	grid = major, legend columns=4
	]

@@

	\addplot[fill=black!90!white] 
	coordinates {
		(0, 0.89)
		(500, 0.37)
		(1000, 0.31)
		(1500, 0.5)
		(2000, 0.38)
	};

>>>>

\begin{figure}
	\begin{subfigure}{.48\textwidth}
		\centering
		\begin{tikzpicture}
		\begin{axis}[
		xlabel=Epochs, 
		ylabel=Training \space MSE,
		width=\textwidth,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		ymax=0.2,
		height=6cm,
		no marks
		]
		\addplot[line width=1pt,solid,color=blue] %
		table{data/ann_tr_loss_3k_our_data_without.txt};
		\addlegendentry{Without GAN}

		\addplot[line width=1pt,solid,color=red] %
		table{data/ann_tr_loss_3k_our_data_with.txt};
		\addlegendentry{With GAN}
		\end{axis}
		\end{tikzpicture}
	\end{subfigure}

@@

\begin{figure}
	\centering
	\begin{tikzpicture}[]
	\begin{axis}[
	ybar, axis x line=bottom, xlabel=Augmented samples, 
	xmin=-100,xmax=3100,
	ymin=0,ymax=1,
	width=0.48\textwidth, height=5cm,
	axis y line=left, ylabel=MSE, 
	legend cell align=left,
	legend style={draw=none, at={(0.5,-0.25)},anchor=north,/tikz/every even column/.append style={column sep=1.0cm}}, 
	ylabel near ticks, ylabel shift={-5pt},
	grid = major, legend columns=4
	]

@@

	\addplot[fill=black!90!white] 
	coordinates {
		(0, 0.89)
		(250, 0.72)
		(500, 0.37)
		(750, 0.43)
		(1000, 0.31)
		(1250, 0.37)
		(1500, 0.5)
		(2000, 0.38)
		(2500, 0.53)
		(3000, 0.92)
	};
